\chapter*{Acknowledgements}
In this line of work, no man is an island, and this thesis is no exception.
I am greatly indebted to many others who have contributed in no small part to my development as both a person and a scientist throughout my tenure in graduate school.

I would first like to thank my thesis advisor, Dr.\ Reina Maruyama.
Throughout my PhD, she has consistently pushed me to be a more precise and technical scientist and student, and I have appreciated the space she has given me in grad school to push my own boundaries in research yet also honing in on tasks that suit my strengths and expand my skills.
I also certainly would like to thank her for allowing me to spend time outside of the lab to focus on my other passions in science education and outreach, which have made me a better scientist and person.

I would also like to thank Drs.\ Karsten Heeger and Tom Wise for their advice and support, particularly after countless meetings and nights working on the calibration system for CUORE.
Observing their problem-solving and management skills certainly taught me a lot about what it means to be a scientist and how to effectively be a scientist working on a large-scale team.

I must also thank my fellows with whom I've spent many hours deep in the foxhole of research, particularly Dr.\ Jeremy Cushman, Dr.\ Danielle Speller, Dr.\ Kyungeun Lim, Dr.\ Tom Langford, Jeremy Gaison, William Thompson, and Dr.\ Nic Chott. It has been a real blessing to have had such fun, hardworking, and sociable coworkers.
I have also been fortunate enough to supervise many enthusiastic undergrads, including Byron Daniel, Surya Dutta, Katie Melbourne, Ivy Wanta, and Nikita Dutta.

Outside of research, I would never had been able to keep my sanity nor have such a fantastic experience in grad school except for the sustained efforts and friendship of Dr.\ Stefan Krastanov, Dr.\ Meredith Powell, Sean Raley, Dr.\ Bridget Hegarty, Peter Williams, Dr.\ James Ingolby, Dr.\ Tonima Ananna, and many others not listed here.
I also would like to express gratitude to the hundreds of students I've had the fortune to teach at Yale.
The many late nights and weekends I spent working with you hardly felt like work at all.

My profound gratitude goes out to my parents for providing me with unfailing support and encouragement throughout my two-and-a-half decades of education, from preschool all the way through graduate school.
Last, and certainly not least, my love and thanks go out to my girlfriend and partner Valerie Cowan for challenging and inspiring me in my research, my personal goals, and everything in between.

\hfill

This accomplishment would not have been possible without them. Thank you all.

\RaggedRight Christopher Davis
